Curve Average \\ {\large Project 3 for CS 6491: Computer Graphics}

### 2015-11-02 paper/paper.tex
Minor changes and suggestions

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
    minimum height=3em, minimum width=6em]
\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
\tikzstyle{input} = [coordinate]
\tikzstyle{output} = [coordinate]
\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
% \renewcommand{\algorithmicrequire}{\textbf{Input:}}
% \renewcommand{\algorithmiccomment}[1]{\ \ // #1} % C-like // Comments

@@

%\title{Simulating elastic spheres without external forces}
%\subtitle{Project 1 for class CS6491 Computer Graphics}
\title{Curve Average \\
	{\large Project 3 for class CS6491 Computer Graphics}}
%\author{Sebastian Weiss}
\author{Sebastian Weiss, Can Erdogan \\ \today}
%\date{\today}

@@

We provide a framework for editing the control curve and visualizing the curve average.
More specific, we support the following features: 
\begin{itemize}
	\item Moving the control points of the two input curve
	\item Displaying the curve average with or without geodesic sampling
	\item Displaying the closest projections
	\item Displaying the circular arc and animating the curve average along it
	\item Showing the inflation tube, the envelope of the smallest spheres
\end{itemize}
We now describe the single features in more detail

@@

As you can see, without geodesic sampling, the distances between the samples of the curve average are almost equispaced, but the closest projections on the control curve, indicated by the circular arcs, vary greatly in the distances. With geodesic sampling turned on, the curve average is sampled in that way that the sum of the distances between two consecutive closest projects on the control curves is constant. However, this leads to large variation of the distances of the curve average samples.

@@

\subsection{Circular arc}
Instead of displaying the closest projections as straight lines, we could also draw them using circular arcs.
\begin{figure}[ht!] 
  \centering
	\begin{tikzpicture}[scale=0.5]
		\coordinate[label=right:P] (P) at (0,0);
		\coordinate[label=left:A] (A) at (-6,-2);
		\coordinate[label=right:B] (B) at (6,-2);
		\coordinate[label=right:C] (C) at (0,-20);
		\draw (P)--(A); %closest projections
		\draw (P)--(B);
		\draw[blue,thick] (6.4,-0.8) coordinate -- (5.6,-3.2) coordinate; %parts of the control curve
		\draw[green,thick] (-6.4,-0.8) coordinate -- (-5.6,-3.2) coordinate;
		\draw (-6.2,-1.4) coordinate -- (-5.6,-1.2) coordinate -- (-5.2,-2.4) coordinate -- (-5.8,-2.6) coordinate; % right angles
		\draw (6.2,-1.4) coordinate -- (5.6,-1.2) coordinate -- (5.2,-2.4) coordinate -- (5.8,-2.6) coordinate;
		\path[blue,thick] (6.4,-0.8) coordinate edge[out=70,in=-120] (6.8,1) coordinate; % control curve
		\path[blue,thick] (5.6,-3.2) coordinate edge[out=250,in=100] (5.8,-5) coordinate;
		\path[green,thick] (-6.4,-0.8) coordinate edge[out=110,in=-120] (-7,1) coordinate;
		\path[green,thick] (-5.6,-3.2) coordinate edge[out=290,in=80] (-5,-5) coordinate;
		\path[black,thick] (0,0) coordinate edge[out=90,in=-70] (-0.2,1) coordinate; % average curve
		\path[black,thick] (0,0) coordinate edge[out=-90,in=110] (0.2,-3) coordinate;
		\draw (A)--(C); %circle sides
		\draw (B)--(C);
		\coordinate[label=left:r] (r) at (-4,-8);
		\draw[red,thick] ([shift=(71.567:19)] 0,-20) arc (71.567:108.435:19); %circular arc
		\tikzset{mypoints/.style={fill=white,draw=black,thick}} %coordinate points
		\fill[mypoints] (P) circle (5.0pt);
		\fill[mypoints] (A) circle (5.0pt);
		\fill[mypoints] (B) circle (5.0pt);
		\fill[mypoints] (C) circle (5.0pt);
	\end{tikzpicture}
	\caption{circular arc}
	\label{fig:CircularArc}
\end{figure}
In Fig.\ref{fig:CircularArc}, you can see parts of the two input curves in green and blue and the curve average in black in the middle. The current trace point is $P$ and the closest projections of $P$ on the control points are $A$ and $B$. \\
We can now construct a unique circle in 3d with center $C$ and radius $r$ that goes through $A$ and $B$, the tangents at these points are $AP$ and $BP$ and lies in the convex hull of $A$,$B$ and $P$.

@@

We present a different approach now. Instead of drawing circles orthogonal to the tangents, we directly take the vectors $P_i A_i$ and rotate them around $T_i$. This technique is visualized in Fig.\ref{fig:InflationDrawing}. We rotate $P_i A_i$ as described in Eq.\ref{eq:Rot} the whole $360^{\circ}$. At $180^{\circ}$, the vector becomes $P_i B_i$. We then sample the circles at constant angles and connect samples with the same angle, leading to the tube as shown in Fig.\ref{fig:Inflation}a.

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
    minimum height=3em, minimum width=6em]
\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
\tikzstyle{input} = [coordinate]
\tikzstyle{output} = [coordinate]
\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
% \renewcommand{\algorithmicrequire}{\textbf{Input:}}
% \renewcommand{\algorithmiccomment}[1]{\ \ // #1} % C-like // Comments
\usepackage{color}
%\newcommand{}{\color{blue}}
\newcommand{\cre}{\color{red}}
\newcommand{\cbl}{\color{black}}

@@

%\title{Simulating elastic spheres without external forces}
%\subtitle{Project 1 for class CS6491 Computer Graphics}
\title{Curve Average \\
	{\large Project 3 for CS 6491: Computer Graphics}}
%\author{Sebastian Weiss}
\author{Sebastian Weiss, Can Erdogan \\ \today}
%\date{\today}

@@

We provide a framework for editing the control curve and visualizing the curve average.
More specific, we support the following features: 
\begin{itemize}
	\item Moving the control points of the two input curve
	\item Displaying the curve average with or without geodesic sampling
	\item Displaying the closest projections
	\item Displaying the circular arc and animating the curve average along it
	\item Showing the inflation tube, the envelope of the smallest spheres
\end{itemize}
We now describe the \cre single \cbl features in more detail.

@@

\cre As you can see, \cbl without geodesic sampling, the distances between the samples of the curve average are almost equispaced, but the closest projections on the control curve, indicated by the circular arcs, vary greatly in the distances. With geodesic sampling turned on, the curve average is sampled in that way that the sum of the distances between two consecutive closest projects on the control curves is constant. However, this leads to large variation of the distances of the curve average samples.

@@

\subsection{Circular arc}
Instead of displaying the closest projections as straight lines, we could also draw them using circular arcs.
\begin{figure}[ht!] 
  \centering
	\begin{tikzpicture}[scale=0.5]
		\coordinate[label=right:P] (P) at (0,0);
		\coordinate[label=left:A] (A) at (-6,-2);
		\coordinate[label=right:B] (B) at (6,-2);
		\coordinate[label=right:C] (C) at (0,-20);
		\draw (P)--(A); %closest projections
		\draw (P)--(B);
		\draw[blue,thick] (6.4,-0.8) coordinate -- (5.6,-3.2) coordinate; %parts of the control curve
		\draw[green,thick] (-6.4,-0.8) coordinate -- (-5.6,-3.2) coordinate;
		\draw (-6.2,-1.4) coordinate -- (-5.6,-1.2) coordinate -- (-5.2,-2.4) coordinate -- (-5.8,-2.6) coordinate; % right angles
		\draw (6.2,-1.4) coordinate -- (5.6,-1.2) coordinate -- (5.2,-2.4) coordinate -- (5.8,-2.6) coordinate;
		\path[blue,thick] (6.4,-0.8) coordinate edge[out=70,in=-120] (6.8,1) coordinate; % control curve
		\path[blue,thick] (5.6,-3.2) coordinate edge[out=250,in=100] (5.8,-5) coordinate;
		\path[green,thick] (-6.4,-0.8) coordinate edge[out=110,in=-120] (-7,1) coordinate;
		\path[green,thick] (-5.6,-3.2) coordinate edge[out=290,in=80] (-5,-5) coordinate;
		\path[black,thick] (0,0) coordinate edge[out=90,in=-70] (-0.2,1) coordinate; % average curve
		\path[black,thick] (0,0) coordinate edge[out=-90,in=110] (0.2,-3) coordinate;
		\draw (A)--(C); %circle sides
		\draw (B)--(C);
		\coordinate[label=left:r] (r) at (-4,-8);
		\draw[red,thick] ([shift=(71.567:19)] 0,-20) arc (71.567:108.435:19); %circular arc
		\tikzset{mypoints/.style={fill=white,draw=black,thick}} %coordinate points
		\fill[mypoints] (P) circle (5.0pt);
		\fill[mypoints] (A) circle (5.0pt);
		\fill[mypoints] (B) circle (5.0pt);
		\fill[mypoints] (C) circle (5.0pt);
	\end{tikzpicture}
	\caption{circular arc}
	\label{fig:CircularArc}
\end{figure}
In Fig.\ref{fig:CircularArc}, you can see parts of the two input curves in green and blue and the curve average in black in the middle. The current trace point is $P$ and the closest projections of $P$ on the control points are $A$ and $B$. \\
We can now construct a unique \cre circle \cbl in $\mathbf{R}^3$ with center $C$ and radius $r$ that goes through $A$ and $B$, the tangents at these points are $AP$ and $BP$ and lies in the convex hull of $A$,$B$ and $P$.

@@

\cre Create a new section? \cbl We present a different approach now. Instead of drawing circles orthogonal to the tangents, we directly take the vectors $P_i A_i$ and rotate them around $T_i$. This technique is visualized in Fig.\ref{fig:InflationDrawing}. We rotate $P_i A_i$ as described in Eq.\ref{eq:Rot} the whole $360^{\circ}$. At $180^{\circ}$, the vector becomes $P_i B_i$. We then sample the circles at constant angles and connect samples with the same angle, leading to the tube as shown in Fig.\ref{fig:Inflation}a.
